Appendix

### 2022-11-06 paper/appendix.Rmd
Use tar_load for figure path

```
```{r tps10, fig.cap=tps10_cap}
knitr::include_graphics(here::here("figures", "p_hist_site_tps10.pdf"))
```

```{r}
rand_sim_cap <- paste0(
  "Simulations of (a) species and (b) nodes extinctions in the metaweb according
  to three scenarios: random extinction sequence, decreasing trophic level,
  increasing trophic level."

)
```

```{r ext, fig.cap=rand_sim_cap}
knitr::include_graphics(here::here("figures", "tot_ext_sim.pdf"))
```

@@

```{r cor, fig.cap=cor_cap}
knitr::include_graphics(here::here("figures", "p_corr.pdf"))
```

@@

```{r, fig.cap=obs_fit_cap}
knitr::include_graphics(here::here("figures", "p_obs_fit.pdf"))
```

@@

```{r}
tar_load(c(pca_table, op_table, com_metric_tab))
tab_quanti <- purrr::map_dfr(
  list(com_metric_tab, op_table, pca_table),
  function(x) {colnames(x)[1] <- "Variable"; x}
)
purrr::map_int(list(com_metric_tab, op_table, pca_table), nrow)

>>>>

```
```{r tps10, fig.cap=tps10_cap}
tar_load(figStps10)
knitr::include_graphics(figStps10)
```

```{r}
rand_sim_cap <- paste0(
  "Simulations of (a) species and (b) nodes extinctions in the metaweb according
  to three scenarios: random extinction sequence, extinction sequence by decreasing order of trophic level,
 extinction sequence by increasing order of trophic level. The black line
 represents the prediction of a GAM model for the random extinction sequences (N = 50)."
)
```

```{r ext, fig.cap=rand_sim_cap}
tar_load(figSext)
knitr::include_graphics(figSext)
```

@@

```{r cor, fig.cap=cor_cap}
tar_load(figcorr)
knitr::include_graphics(figcorr)
```

@@

```{r, fig.cap=obs_fit_cap}
tar_load(figSobsfit)
knitr::include_graphics(figSobsfit)
```

@@

```{r}
tar_load(c(pca_table, op_table, com_metric_tab))
tab_quanti <- purrr::map_dfr(
  list(com_metric_tab, op_table, pca_table),
  function(x) {colnames(x)[1] <- "Variable"; x}
)
#purrr::map_int(list(com_metric_tab, op_table, pca_table), nrow)
